Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
fixing mistake.

Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.
For instance, some packages, including {\tt filepath}, 
{\tt containers}, {\tt bytestring} and {\tt text}, adopt this style.
Here is an example from the latter.

>>>>

Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.
For instance, some packages, including {\tt containers}, {\tt filepath}, 
{\tt bytestring} and {\tt text}, adopt this style.
Here is an example from the first one.
